### 2020-07-14 nb/analysis_in_R.Rmd
get mXG for all leagues

        state_probabilities <- matrix(NA,nrow=max_steps+1,ncol=ncol(transition_matrix),dimnames=list(0:max_steps,(ncol(transition_matrix)-1):0))
        vector <- rep(0,ncol(transition_matrix))

@@

    season_graph <- graph_from_adjacency_matrix(season_adjacency_matrix)
    season_transition <- TransitionMatrix(season_graph)
    seasonXST <- ExpectedScoringTime(season_transition)
    avg_events_per_game <- nrow(events)/380
    mXG <- sort(avg_events_per_game/seasonXST, decreasing=T)

    return(mXG)
}
```

@@

```{r}
liverpool_adj <- SeasonAdjacencyMatrix(events,'Liverpool')

```{r}
mXG <- MarkovExpectedGoals(events, liverpool_adj)
```

```{r}
mXG
```

```{r}
GoalProbabilities(liverpool_adj)
```

```{r}
sort(liverpool_adj[,'Goal'],T)
```

>>>>

        state_probabilities <- matrix(NA,nrow=max_steps+1,ncol=ncol(transition_matrix),
                                      dimnames=list(0:max_steps,(ncol(transition_matrix)-1):0))
        vector <- rep(0,ncol(transition_matrix))

@@

    season_graph <- graph_from_adjacency_matrix(season_adjacency_matrix)
    season_transition <- TransitionMatrix(season_graph)
    seasonXST <- ExpectedScoringTime(season_transition)
    seasonMXG <- 1/seasonXST
    normalize <- seasonMXG/(mean(seasonMXG))
    avg_events_per_game <- nrow(events)/380
    scale <- normalize * avg_events_per_game - avg_events_per_game
    sorted <- sort(scale, decreasing=T)

    return(sorted)
}
```

@@

```{r}
leagueMXG <- function(events){

    all_mXG <- c()
    teams <- unique(events$team)

    for (team in teams){

        season_adjacency_matrix <- SeasonAdjacencyMatrix(events, team)
        mXG <- MarkovExpectedGoals(events, season_adjacency_matrix)

        all_mXG <- append(all_mXG, mXG)

    return(all_mXG)
}
```

```{r}
mXG <- c()
leagues = c('England','France','Germany','Italy','Spain')
for (league in leagues){
    events <- LoadAndScaleData(league)
    mXG <- append(mXG, leagueMXG(events))
}
```

```{r}
sort(mXG,T)
```
